### 2019-11-28 Mathematical Statistics/ms_ch_04.rmd
mathematical statistics
mathematical statistics

#### Sampling Distributions

@@

p <- c(1, 2, 5, 6, 10, 12)
c <- combinations(v = p, n = 6, r = 3)
m <- apply(c, 1, median)

ggplot(data.table(value = m), aes(value, fill = ..count..)) +
   geom_histogram(bins = 30) +
   labs(title = "Median Sampling Distribution of p")

@@

Median of p = __`r median(p)`__. Mean of Medians of p = __`r mean(m)`__

@@

What is the mean of the sampling distribution?

@@

@@

p <- c(3, 6, 7, 9, 11, 14)

@@

>>>>

@@

p <- c(1, 2, 5, 6, 10, 12)
c <- combinations(v = p, n = 6, r = 3)
t <- apply(c, 1, median)

ggplot(data.table(value = t), aes(value, fill = ..count..)) +
   geom_histogram(bins = 30) +
   labs(title = "Median Sampling Distribution of p")

@@

Median of p = __`r median(p)`__. Mean of Medians of p = __`r mean(t)`__

\newpage

@@

p <- c(3, 6, 7, 9, 11, 14)
c <- combinations(v = p, n = 6, r = 3)
t <- apply(c, 1, min)

ggplot(data.table(value = t), aes(value, fill = ..count..)) +
   geom_histogram(bins = 30) +
   labs(title = "Minimum Sampling Distribution of p")

What is the mean of the sampling distribution? __`r mean(t)`__

@@

This is an estimation of the minimum, which is: __`r min(p)`__

\newpage

### 4.3

Let _A_ denote the population {1, 3, 4, 5} and _B_ the population {5, 7, 9}.

@@

permutations( v = p, n = 2, r = 2, repeats.allowed = T)

combinations( v = p, n = 3, r = 2, repeats.allowed = T)

A <- c(1, 3, 4, 5)
B <- c(5, 7, 9)

@@

Let _X_ be a random value from _A_, and _Y_ and random value from _B_.

a.) Find the sampling distribution of _X + Y_.

p <- c(3, 4, 6, 6)

sample.size <- 2
perm <- permutations( length(p), sample.size, repeats.allowed = T)

d <- data.table( c1 = p[perm[, 1]], c2 = p[perm[, 2]])
d[, m := (c1 + c2) / 2]

b.) In this example, does the sampling distribution depend on whether you sample with or without replacement?

_No._

Why or why not?

_Because 5 in is both sets._

c.) Compute the mean of the values for each of _A_ and _B_ and the values in the sampling distribution of _X + Y_.

How are the means related?

d.) Suppose you draw a random value from _A_ and a random value from _B_.

What is the probability that the sum is 13 or larger?
